LAGOS lake depth

### 2020-02-13 figures/00_maps.Rmd
adjust fig dimensions

gg_colocated

# gg_shapeclass <-

```

>>>>

gg_colocated
```

```{r gg_shapeclass, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide'}
dt           <- st_read("../data/gis.gpkg", "dt", quiet = TRUE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  distinct(lagoslakeid, .keep_all = TRUE)
dt_withshape <- read.csv("../data/lagosus_depth_predictors.csv", 
               stringsAsFactors = FALSE) %>%
  dplyr::distinct(lagoslakeid, shape_class) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  mutate(lagoslakeid = as.character(lagoslakeid))
dt           <- inner_join(dt, dt_withshape) %>%
  arrange(desc(shape_class))

gg_shapeclass <- ggplot() + 
    geom_sf(data = st_as_sfc(st_bbox(dt_bathy)), alpha = 1, size = 0.6, 
          color = "black", fill = "#1D9DCF") +
    geom_sf(data = st_crop(states_all, st_as_sfc(st_bbox(dt_bathy))), fill = "gray", color = "black", size = 0.3) +
    geom_sf(data = st_crop(states_focal, st_as_sfc(st_bbox(dt_bathy))), fill = "white", color = "black", size = 0.4) + 
    geom_sf(data = dplyr::filter(dt, shape_class == "convex"), aes(color = shape_class),
                    size = 0.03, alpha = 0.3) +
    geom_sf(data = dplyr::filter(dt, shape_class != "convex"), aes(color = shape_class),
                    size = 0.07, alpha = 0.8) +
    labs(color = "Shape class   ") +
    coord_sf(xlim = c(-103.81483, -67.10548), ylim = c(37.5, 48.72102)) +
    theme_void()

gg_shapeclass

# table of shape_class by state
# st_drop_geometry(dt) %>%
#   group_by(lake_state, shape_class) %>%
#   count() %>%
#   tidyr::pivot_wider(names_from = shape_class, values_from = n)
```

```{r 00_map_bathy, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=6}
cowplot::plot_grid(gg_bathy, 
                   gg_shapeclass, 
                   ncol = 1)
```

### 2020-02-13 figures/00_qa.Rmd
adjust fig dimensions

```{r lgnemanual-vs-bathy-depth, fig.height=3}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

@@

cowplot::plot_grid(gg_max + theme(legend.position = "none"), 
                   gg_mean + theme(axis.title.y = element_blank()), 
                   rel_widths = c(0.7, 1))
```

>>>>

```{r lgnemanual-vs-bathy-depth, fig.height=2.7, fig.width=6}
dt <- read.csv("../data/lagosus_depth.csv", stringsAsFactors = FALSE)

@@

cowplot::plot_grid(gg_max + theme(legend.position = "none"), 
                   gg_mean + theme(axis.title.y = element_blank()), 
                   rel_widths = c(0.8, 1))
```
